\subsection{Serial Communication and the Great Horse Race}
The input of the system is handled using MATLAB. This is appealing for several reasons 
1)We can immedietly visualise and process the sound array that we get, making it easy to debug. 
2)We can use the inbuilt system microphone. 
MATLAB by default offers several different ways to get this Audio data, the lowest resolution being a 1000Hz Sampling frequency and 8bit sampling, using the audiorecorder object. Once we record the relevent sample, we extract an array with this data and after doing some basic filtering, to remove any high frequency noise that may affect the signal, we send the data to the Arduino via the Serial port. 

The important part here is understanding how the serial communication with the Arduino works. The serial port can only send data character by charater to the Arduino and waits for it to be processed. Therefore the processing of the integers is done as follows: 
\begin{enumerate}
    \item Collect multiple audio samples from the microphone. We take 2000 datapoints,assuming a periodic sample. The points are all int8
    \item Apply a filter to remove any peaks above \(\pm7\) to ensure that the data doesn't overflow in the arduino. Then we apply a Moving average filter by taking 3 200 datapoint samples from the 2000 datapoints to remove any anamolous noise in the data
    \item In order to communicate this data, we convert the integer Array in MATLAB to strings using the int2str method so that it can be sent via the Serial port. The terminator that we use is the character '\n'
    \item We open the serial monitor and send the data character by character using the fprintf function in Matlab
    \item We check for available data in the Arduino using the Serial.available() function
    \item Then we read the data into an array in Arduino using the Serial.parseInt() function. We wait for 2 bytes to arrive and store them in a single byte on the arduino to work with our processing scheme
    \item When all the expected data (200 points) are read, stop recording and do the processing to find the matching frequencies. 
    \item Send the frequencies back to MATLAB to print using the Serial port. 
\end{enumerate}
However, we ran into some issues here, where several values were not detected by the Arduino. We tried multiple approaches to solve this 
\begin{enumerate}
    \item We increased the Baud rate to 115200 to ensure that the transmission wasn't causing any loss of data. 
    \item We added a small delay of 30ms between subsequent transmissions to ensure that the Arduino had time to process the data
    \item The Serial protocol has a buffer that stores the incoming values before they are processed by the Arduino. In the Arduino Uno, this SERIAL_RX_BUFFER Memory that stores the incoming data from the Serial Port is only 64 bytes. We changed the source code to make the buffer 128 bytes in the file HardwareSerial.h so that more characters could be stored without losing them in transmission
\end{enumerate}
In order to ensure that this method is working correctly we have several checks 
\begin{enumerate}
    \item We ran a simple program that turns the pin13 LED On and Off based on whether the character it recieved was 0 or -7
    \item IN our main code, pin13 is HIGH when waiting for data and recording. When all the expected data has been found, it stops glowing 
    \item We also plot the raw data that we get from the Mic to ensure that a reasonable waveform has been detected
\end{enumerate}
The code for testing the glowing of the LEDs is found here: 
\begin{lstlisting}
    int led = 13;
String text;
int ki;
void setup() {
                //pinMode(led, OUTPUT);
                Serial.begin(9600);
                ki = 0;
}
void loop() { 
  if (Serial.available()){
                    text = Serial.readStringUntil('$');
                                           ki = text.toInt(); 
                                           text = Serial.readStringUntil('$');
                                           ki = text.toInt();
                                                   
                                              
  }}

\end{lstlisting}
The MATLAB code for controlling this unit is found here: 
\begin{lstlisting}
    Arduino = serial("COM4","BaudRate",9600);
    fopen(Arduino) %This opens a monitor
    fprintf(Arduino,'%s$',int2str(0));
    fprintf(Arduino,'%s$',int2str(-7));
    fclose(Arduino);

\end{lstlisting}

